---
title: "BiocSwirl - Course Installation"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{BiocSwirl Course Installation}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---


## BiocSwirl
BiocSwirl is a series of in-depth swirlify generated courses used to teach bioinformatics workflows in R/Bioconductor using an interactive and easy to digest format. 

For more information visit https://github.com/biocswirl-dev-team/BiocSwirl.

### BiocSwirl Installation
```{r, eval = FALSE}
install.packages("devtools")
library(devtools)
devtools::install_github("biocswirl-dev-team/BiocSwirl")
```


### Course Installation

```{r, eval = FALSE}
# list all available BiocSwirl courses
list_courses()

# install selected course. 
# copy name from output of list_courses()
load_course(course ='RNAseq')
```

### Start Course
To start the course environment, excute the command below. No parameters are necessary. The command will start an interactive environment that will allow you to navigate to your course.
```{r, eval = FALSE}
start_course()
```

### Uninstall course
```{r, eval=FALSE}
# list all installed BiocSwirl courses
installed_courses()

# uninstall selected course
uninstall_course(course = 'RNAseq')

# uninstall all BiocSwirl courses 
# this will not uninstall other swirl courses
uninstall_all_courses()
```

